---
title: "fticr"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      collapse = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      comment = "#>",
                      fig.path = ("markdown/fticr/"))
```

```{r load}
library(here)
source(here("code/0-packages.R"))
theme_set(theme_bw())
pal = pnw_palette("Bay", 3)

```

```{r files}
data_long = read.csv(here("data/processed/fticr_long_core.csv.gz"))
data = read.csv(here("data/processed/fticr_long_key.csv.gz")) %>% 
   #filter(n>2) %>% 
   mutate(Homogenization = factor(Homogenization, levels = c("Intact", "Homogenized")),
         Amendments = factor(Amendments, levels = c("control", "C", "N")))
data_long_trt = read.csv(here("data/processed/fticr_long_trt.csv.gz"))

meta = read.csv(here("data/processed/fticr_meta.csv"))
meta_hcoc = 
  meta %>% 
  select(formula, HC, OC)
```

## HYPOTHESES

- C amendments will increase diversity of SOM molecules
- C amendments will cause a depletion of aromatic molecules, especially in fine pores
- Homogenization will increase (a) total peaks, (b) diversity of peaks, (c) aromatic peaks


We selected only peaks seen in >1 of the 4 replicates (i.e. n = 2 or 3 or 4)

---


### fticr domains  


```{r domains, fig.height=4, fig.width=6}
# domains ggplot
gg_vankrev(meta, aes(x = OC, y = HC, color = class))

classes = read.csv(here("data/fticr_meta_classes.csv"))

classes %>% 
   #filter(!compounds == "unnamed") %>% 
   left_join(select(meta, Mass, HC, OC), by = "Mass") %>% 
   gg_vankrev(aes(x = OC, y = HC, color = compounds))

```

**aromatic peaks**  

```{r ai_domains, fig.height=4, fig.width=6}
meta %>% 
   select(formula, class, HC, OC, AImod) %>% 
   mutate(AImod_abs = abs(AImod),
          arom = if_else(AImod>0.67, "condensed aromatic",
                         if_else(AImod>0.5, "aromatic", NA_character_))) %>% 
   filter(!is.na(arom)) %>% 
   ggplot(aes(x = OC, y = HC, color = arom)) +
    geom_point(size=2, alpha = 0.2) + # set size and transparency
    ylab("H/C") +
    xlab("O/C") +
    xlim(0,1.25) +
    ylim(0,2.5) +
   scale_color_manual(values = pnw_palette("Sailboat",2))+
    geom_segment(x = 0.0, y = 1.5, xend = 1.2, yend = 1.5,color="black",linetype="longdash") +
    geom_segment(x = 0.0, y = 0.7, xend = 1.2, yend = 0.4,color="black",linetype="longdash") +
    geom_segment(x = 0.0, y = 1.06, xend = 1.2, yend = 0.51,color="black",linetype="longdash") +
   
   annotate("text", label = "aliphatic", x = 0.2, y = 1.75)+
   annotate("text", label = "highly unsaturated/ \n lignin-like", x = 0.2, y = 1.25)+
   annotate("text", label = "aromatic", x = 0.2, y = 0.85)+
   annotate("text", label = "condensed aromatic", x = 0.2, y = 0.35)+
   guides(colour = guide_legend(override.aes = list(alpha=1)))
```


---

### van krevelens  

```{r vk_baseline, fig.width=5, fig.height=5}
data %>%
   left_join(meta_hcoc, by = "formula") %>%
   filter(Moisture=="fm" & Wetting == "groundw" & Amendments=="control" & 
             Homogenization=="Intact" & Suction!=15 ) %>% 
   gg_vankrev(aes(x = OC, y = HC, color = as.character(Suction)))+
   stat_ellipse()+
   scale_color_manual(values = PNWColors::pnw_palette("Bay",3))+
   labs(title = "baseline (fm, groundw, non-amended)")+
   theme_kp()+
   NULL
```



```{r vk_pores, fig.width=10, fig.height=5}
data %>%
   left_join(meta_hcoc, by = "formula") %>%
   filter(Suction=="1.5") %>% 
   gg_vankrev(aes(x = OC, y = HC, color = Amendments))+
   stat_ellipse()+
   scale_color_manual(values = pal)+
   facet_grid(Homogenization~Moisture+Wetting)+
   labs(title = "1.5 kPa")+
   #theme(legend.position = "none")+
   NULL

data %>%
   left_join(meta_hcoc, by = "formula") %>%
   filter(Suction=="15") %>% 
   gg_vankrev(aes(x = OC, y = HC, color = Amendments))+
   stat_ellipse()+
   scale_color_manual(values = pal)+
   facet_grid(Homogenization~Moisture+Wetting)+
   labs(title = "15 kPa")+
   #theme(legend.position = "none")+
   NULL

data %>%
   left_join(meta_hcoc, by = "formula") %>%
   filter(Suction=="50") %>% 
   gg_vankrev(aes(x = OC, y = HC, color = Amendments))+
   stat_ellipse()+
   scale_color_manual(values = pal)+
   facet_grid(Homogenization~Moisture+Wetting)+
   labs(title = "50 kPa")+
   #theme(legend.position = "none")+
   NULL
```

---

### relative abundances

```{r}
relabund_trt = read.csv(here("data/processed/fticr_relabund_trt.csv")) %>% 
   dplyr::mutate(class = factor(class, levels = 
                          c("aliphatic", "aliphatic+N","unsaturated",
                            "aromatic","condensed_arom", "other")),
                 Amendments = factor(Amendments, levels = c("control", "C", "N")),
                 Homogenization = factor(Homogenization, levels = c("Intact", "Homogenized")),
                 Moisture = factor(Moisture, levels = c("fm", "drought"))) %>% 
   filter(!Suction=="15")
```


```{r fticr_relabund}
relabund_trt %>%  
   ggplot(aes(x = Amendments, y = rel_abund, fill = class))+
   geom_bar(stat = "identity")+
   scale_fill_viridis_d(option = "inferno")+
   labs(x = "percent saturation",
        y = "relative abundance (%)")+
   facet_grid(Suction+Homogenization~Moisture+Wetting)+
   NULL
```

```{r NOSC, fig.height=6, fig.width=10}
meta_nosc = 
   meta %>% 
   select(formula, NOSC)

data %>% 
   left_join(meta_nosc, by = "formula") %>% 
   ggplot(aes(x = Amendments, y = NOSC, fill = Amendments))+
   geom_violin()+
   geom_boxplot(width=0.2, coef=0, outlier.shape = NA, fill = "white")+
#   geom_dotplot(binaxis = "y", size=1)+
   scale_fill_manual(values = pal)+
   labs(x = "",
        y = "NOSC")+
   theme(legend.position = "none")+
   facet_grid(Suction~Homogenization+Moisture+Wetting)+
   NULL
```

---

### PEAKS

```{r fticr_peaks_, eval=FALSE}
meta_classes = 
  meta %>% 
  select(formula, class)

fticr_key = read.csv(here("data/processed/fticr_key.csv")) %>% 
   distinct(SampleAssignment, Moisture, Wetting, Amendments, Suction, Homogenization)
fticr_data_key = read.csv(here("data/processed/fticr_long_key.csv.gz"))

fticr_peaks = 
  fticr_data_key %>% 
  left_join(meta_classes, by = "formula") %>% 
  group_by(FTICR_ID, SampleAssignment, class) %>% 
  summarize(n = n()) %>% 
  ungroup() %>% 
  group_by(FTICR_ID, SampleAssignment) %>% 
  mutate(total = sum(n)) %>% 
  spread(class, n) %>% 
  pivot_longer(-c(FTICR_ID, SampleAssignment),
               names_to = "class") %>% 
  ungroup() %>% 
  group_by(SampleAssignment, class) %>% 
   summarize(peaks = as.integer(mean(value))) %>% 
  #spread(name, peaks) %>% 
   left_join(fticr_key, by = "SampleAssignment") %>% 
   ungroup %>% 
   select(-SampleAssignment) %>% 
   mutate(Amendments = factor(Amendments, 
                              levels = c("control", "C", "N")),
          class = factor(class, levels = 
                          c("aliphatic", "aliphatic+N","unsaturated","aromatic","condensed_arom", "other", "total")))
```


```{r fticr_peaks_tables_, eval=FALSE}
print("1.5 kPa -- INTACT")
fticr_peaks %>% 
   filter(Suction==1.5 & Homogenization=="Intact") %>% 
   spread(Amendments, peaks) %>% 
   select(Moisture, Wetting, class, control, C, N) %>% 
   arrange(Moisture, Wetting) %>%
   knitr::kable()

print("15 kPa -- INTACT")
fticr_peaks %>% 
   filter(Suction==15 & Homogenization=="Intact") %>% 
   spread(Amendments, peaks) %>% 
   select(Moisture, Wetting, class, control, C, N) %>% 
   arrange(Moisture, Wetting) %>%
   knitr::kable()

print("50 kPa -- INTACT")
fticr_peaks %>% 
   filter(Suction==50 & Homogenization=="Intact") %>% 
   spread(Amendments, peaks) %>% 
   select(Moisture, Wetting, class, control, C, N) %>% 
   arrange(Moisture, Wetting) %>%
   knitr::kable()

print("1.5 kPa -- HOMOGENIZED")
fticr_peaks %>% 
   filter(Suction==1.5 & Homogenization=="Homogenized") %>% 
   spread(Amendments, peaks) %>% 
   select(Moisture, Wetting, class, control, C, N) %>% 
   arrange(Moisture, Wetting) %>%
   knitr::kable()

print("15 kPa -- HOMOGENIZED")
fticr_peaks %>% 
   filter(Suction==15 & Homogenization=="Homogenized") %>% 
   spread(Amendments, peaks) %>% 
   select(Moisture, Wetting, class, control, C, N) %>% 
   arrange(Moisture, Wetting) %>%
   knitr::kable()

print("50 kPa -- HOMOGENIZED")
fticr_peaks %>% 
   filter(Suction==50 & Homogenization=="Homogenized") %>% 
   spread(Amendments, peaks) %>% 
   select(Moisture, Wetting, class, control, C, N) %>% 
   arrange(Moisture, Wetting) %>%
   knitr::kable()
```

distinct peaks seen in each treatment type  

<details>
   <summary>click to expand</summary>
   
```{r load_files}
fticr_key = read.csv(here("data/processed/fticr_key.csv")) %>% 
   distinct(SampleAssignment, Moisture, Wetting, Amendments, Suction, Homogenization)
fticr_data_key = read.csv(here("data/processed/fticr_long_key.csv.gz"))
meta_classes = 
  meta %>% 
  select(formula, class)
```

```{r fticr_peaks}
peaks_distinct = 
   fticr_data_key %>% 
   group_by(SampleAssignment) %>% 
   distinct(formula)

peakcounts = 
   peaks_distinct %>% 
   left_join(meta_classes, by = "formula") %>% 
  group_by(SampleAssignment, class) %>% 
  summarize(n = n()) %>% 
  ungroup() %>% 
  group_by(SampleAssignment) %>% 
  dplyr::mutate(total = sum(n)) %>% 
  spread(class, n) %>% 
  pivot_longer(-c(SampleAssignment),
               names_to = "class") %>% 
  ungroup() %>% 
  group_by(SampleAssignment, class) %>% 
   dplyr::summarize(peaks = as.integer(mean(value))) %>% 
  #spread(name, peaks) %>% 
   left_join(fticr_key, by = "SampleAssignment") %>% 
   ungroup %>% 
   select(-SampleAssignment) %>% 
   mutate(Amendments = factor(Amendments, 
                              levels = c("control", "C", "N")),
          class = factor(class, levels = 
                          c("aliphatic", "aliphatic+N","unsaturated","aromatic","condensed_arom", "other", "total")))
```

```{r fticr_peaks_tables}
print("1.5 kPa -- INTACT")
peakcounts %>% 
   filter(Suction==1.5 & Homogenization=="Intact") %>% 
   spread(Amendments, peaks) %>% 
   select(Moisture, Wetting, class, control, C, N) %>% 
   arrange(Moisture, Wetting) %>%
   knitr::kable()

print("15 kPa -- INTACT")
peakcounts %>% 
   filter(Suction==15 & Homogenization=="Intact") %>% 
   spread(Amendments, peaks) %>% 
   select(Moisture, Wetting, class, control, C, N) %>% 
   arrange(Moisture, Wetting) %>%
   knitr::kable()

print("50 kPa -- INTACT")
peakcounts %>% 
   filter(Suction==50 & Homogenization=="Intact") %>% 
   spread(Amendments, peaks) %>% 
   select(Moisture, Wetting, class, control, C, N) %>% 
   arrange(Moisture, Wetting) %>%
   knitr::kable()

print("1.5 kPa -- HOMOGENIZED")
peakcounts %>% 
   filter(Suction==1.5 & Homogenization=="Homogenized") %>% 
   spread(Amendments, peaks) %>% 
   select(Moisture, Wetting, class, control, C, N) %>% 
   arrange(Moisture, Wetting) %>%
   knitr::kable()

print("15 kPa -- HOMOGENIZED")
peakcounts %>% 
   filter(Suction==15 & Homogenization=="Homogenized") %>% 
   spread(Amendments, peaks) %>% 
   select(Moisture, Wetting, class, control, C, N) %>% 
   arrange(Moisture, Wetting) %>%
   knitr::kable()

print("50 kPa -- HOMOGENIZED")
peakcounts %>% 
   filter(Suction==50 & Homogenization=="Homogenized") %>% 
   spread(Amendments, peaks) %>% 
   select(Moisture, Wetting, class, control, C, N) %>% 
   arrange(Moisture, Wetting) %>%
   knitr::kable()
```

</details>


**Peak counts**  


```{r table_total_peak_counts}
peakcounts %>% 
   filter(class=="total" & !Suction == 15) %>% 
   select(-class) %>% 
   mutate(var = paste0(Suction,"-",Amendments),
          var = factor(var, levels = c("1.5-control", "1.5-C", "1.5-N",
                                       "50-control", "50-C", "50-N")), 
          Homogenization = factor(Homogenization, levels = c("Intact", "Homogenized"))) %>% 
   select(-Suction,-Amendments) %>% 
   spread(var, peaks) %>% 
   gt(rowname_col = "row", groupname_col = "Homogenization") %>% 
   tab_spanner(label = "1.5 kPa", columns = contains("1.5")) %>% 
   tab_spanner(label = "50 kPa", columns = contains("50")) %>% 
   tab_header(
    title = md("Total Peaks Present"),
  )
```

```{r table_aromatic_peak_counts}
peakcounts %>% 
   filter(class %in% c("aromatic", "condensed_arom") & !Suction == 15) %>%
   group_by(Suction, Moisture, Wetting, Amendments, Homogenization) %>% 
   summarise(peaks=sum(peaks)) %>% 
   ungroup() %>% 
   #select(-class) %>% 
   mutate(var = paste0(Suction,"-",Amendments),
          var = factor(var, levels = c("1.5-control", "1.5-C", "1.5-N",
                                       "50-control", "50-C", "50-N")),
          Homogenization = factor(Homogenization, levels = c("Intact", "Homogenized"))) %>% 
   select(-Suction,-Amendments) %>% 
   spread(var, peaks) %>% 
   gt(rowname_col = "row", groupname_col = "Homogenization") %>% 
   tab_spanner(label = "1.5 kPa", columns = contains("1.5")) %>% 
   tab_spanner(label = "50 kPa", columns = contains("50")) %>% 
   tab_header(
    title = md("Aromatic Peaks Present")
  )
```


### STATS -- 

#### MANOVA

```{r}
relabund_cores = 
   read.csv(here("data/processed/fticr_relabund_cores.csv")) %>% 
   dplyr::mutate(class = factor(class, levels = 
                          c("aliphatic", "aliphatic+N","unsaturated","aromatic","condensed_arom", "other")),
                 Amendments = factor(Amendments, levels = c("control", "C", "N")),
                 Homogenization = factor(Homogenization, levels = c("Intact", "Homogenized"))) 
```


```{r fticr_manova, eval=FALSE}
relabund_wide = 
  relabund_cores %>% 
  dplyr::select(Core, SampleAssignment, class, relabund, Moisture, Wetting, Suction, Homogenization, Amendments) %>% 
  spread(class, relabund) %>% 
  replace(is.na(.),0)

# create a matrix of all the group columns
relabund_wide$DV = as.matrix(relabund_wide[,8:13])

# since the relative abundances are not strictly independent and all add to 100 %,
# use the isometric log ratio transformation
# http://www.sthda.com/english/wiki/manova-test-in-r-multivariate-analysis-of-variance#import-your-data-into-r

library(compositions)

man = manova(ilr(clo(DV)) ~ Amendments*Moisture*Wetting*Suction*Homogenization, data = relabund_wide)
summary(man)
```

#### PCA 
**intact cores**

<details>   
   <summary>click to expand</summary>
   
```{r fticr_pca_intact}
library(ggbiplot)

relabund_pca=
  relabund_cores %>% 
  select(Core, SampleAssignment, class, relabund, Moisture, Wetting, Suction, Homogenization, Amendments) %>% 
  spread(class, relabund) %>% 
  replace(is.na(.),0) %>% 
  select(-1,)

#
## 0. overall intact----
relabund_pca_num_intact = 
   relabund_pca %>% 
   filter(Homogenization=="Intact") %>% 
   dplyr::select(.,-(1:6))

relabund_pca_grp_intact = 
  relabund_pca %>% 
      filter(Homogenization=="Intact") %>% 
  dplyr::select(.,(1:6)) %>% 
  dplyr::mutate(row = row_number())

pca = prcomp(relabund_pca_num_intact, scale. = T)
#summary(pca)

ggbiplot(pca, obs.scale = 1, var.scale = 1, 
         groups = relabund_pca_grp_intact$Amendments, ellipse = TRUE, circle = F,
         var.axes = TRUE)+
  geom_point(size=5,stroke=1, aes(color = groups, shape = interaction(as.factor(relabund_pca_grp_intact$Moisture),
                                                                      as.factor(relabund_pca_grp_intact$Wetting))))+
   scale_shape_manual(values = c(1, 2, 19, 17))+
   scale_color_manual(values = pal)+
   labs(shape="",
        title = "INTACT")+
   NULL

ggbiplot(pca, obs.scale = 1, var.scale = 1, 
         groups = as.character(relabund_pca_grp_intact$Suction), ellipse = TRUE, circle = F,
         var.axes = TRUE)+
  geom_point(size=5,stroke=1, aes(color = groups, shape = interaction(as.factor(relabund_pca_grp_intact$Moisture),
                                                                      as.factor(relabund_pca_grp_intact$Wetting))))+
   scale_shape_manual(values = c(1, 2, 19, 17))+
   scale_color_manual(values = pal)+
   labs(shape="",
        title = "INTACT")+
   NULL

```

</details>



**homogenized cores**  


<details>  
   <summary>click to expand</summary>


```{r fticr_pca_homo}
#
## 0b. overall homogenized----
relabund_pca_num_Homogenized = 
   relabund_pca %>% 
   filter(Homogenization=="Homogenized") %>% 
   dplyr::select(.,-(1:6))

relabund_pca_grp_Homogenized = 
  relabund_pca %>% 
      filter(Homogenization=="Homogenized") %>% 
  dplyr::select(.,(1:6)) %>% 
  dplyr::mutate(row = row_number())

pca = prcomp(relabund_pca_num_Homogenized, scale. = T)
#summary(pca)

ggbiplot(pca, obs.scale = 1, var.scale = 1, 
         groups = relabund_pca_grp_Homogenized$Amendments, ellipse = TRUE, circle = F,
         var.axes = TRUE)+
  geom_point(size=5,stroke=1, aes(color = groups, shape = interaction(as.factor(relabund_pca_grp_Homogenized$Moisture),
                                                                      as.factor(relabund_pca_grp_Homogenized$Wetting))))+
   scale_shape_manual(values = c(1, 2, 19, 17))+
   scale_color_manual(values = pal)+
   labs(shape="",
        title = "Homogenized")+
   NULL

ggbiplot(pca, obs.scale = 1, var.scale = 1, 
         groups = as.character(relabund_pca_grp_Homogenized$Suction), ellipse = TRUE, circle = F,
         var.axes = TRUE)+
  geom_point(size=5,stroke=1, aes(color = groups, shape = interaction(as.factor(relabund_pca_grp_Homogenized$Moisture),
                                                                      as.factor(relabund_pca_grp_Homogenized$Wetting))))+
   scale_shape_manual(values = c(1, 2, 19, 17))+
   scale_color_manual(values = pal)+
   labs(shape="",
        title = "Homogenized")+
   NULL

```


```{r fticr_pca_indiv}
## 1. 50 & intact ----
relabund_pca_num_50_intact = 
   relabund_pca %>% 
   filter(Suction==50 & Homogenization=="Intact") %>% 
   dplyr::select(.,-(1:6))

relabund_pca_grp_50_intact = 
  relabund_pca %>% 
      filter(Suction==50 & Homogenization=="Intact") %>% 
  dplyr::select(.,(1:6)) %>% 
  dplyr::mutate(row = row_number())

pca = prcomp(relabund_pca_num_50_intact, scale. = T)
#summary(pca)

ggbiplot(pca, obs.scale = 1, var.scale = 1, 
         groups = relabund_pca_grp_50_intact$Amendments, ellipse = TRUE, circle = F,
         var.axes = TRUE)+
  geom_point(size=5,stroke=1, aes(color = groups, shape = interaction(as.factor(relabund_pca_grp_50_intact$Moisture),
                                                                      as.factor(relabund_pca_grp_50_intact$Wetting))))+
   scale_shape_manual(values = c(1, 2, 19, 17))+
   scale_color_manual(values = pal)+
   labs(shape="",
        title = "50 kPa INTACT")+
   NULL

## 2. 15 & intact ----
relabund_pca_num_15_intact = 
   relabund_pca %>% 
   filter(Suction==15 & Homogenization=="Intact") %>% 
   dplyr::select(.,-(1:6))

relabund_pca_grp_15_intact = 
  relabund_pca %>% 
      filter(Suction==15 & Homogenization=="Intact") %>% 
  dplyr::select(.,(1:6)) %>% 
  dplyr::mutate(row = row_number())

pca = prcomp(relabund_pca_num_15_intact, scale. = T)
#summary(pca)

ggbiplot(pca, obs.scale = 1, var.scale = 1, 
         groups = relabund_pca_grp_15_intact$Amendments, ellipse = TRUE, circle = F,
         var.axes = TRUE)+
  geom_point(size=5,stroke=1, aes(color = groups, shape = interaction(as.factor(relabund_pca_grp_15_intact$Moisture),
                                                                      as.factor(relabund_pca_grp_15_intact$Wetting))))+
   scale_shape_manual(values = c(1, 2, 19, 17))+
   scale_color_manual(values = pal)+
   labs(shape="",
        title = "15 kPa INTACT")+
   NULL

## 3. 1.5 & intact ----
relabund_pca_num_1_intact = 
   relabund_pca %>% 
   filter(Suction==1.5 & Homogenization=="Intact") %>% 
   dplyr::select(.,-(1:6))

relabund_pca_grp_1_intact = 
  relabund_pca %>% 
      filter(Suction==1.5 & Homogenization=="Intact") %>% 
  dplyr::select(.,(1:6)) %>% 
  dplyr::mutate(row = row_number())

pca = prcomp(relabund_pca_num_1_intact, scale. = T)
#summary(pca)

ggbiplot(pca, obs.scale = 1, var.scale = 1, 
         groups = relabund_pca_grp_1_intact$Amendments, ellipse = TRUE, circle = F,
         var.axes = TRUE)+
  geom_point(size=5,stroke=1, aes(color = groups, shape = interaction(as.factor(relabund_pca_grp_1_intact$Moisture),
                                                                      as.factor(relabund_pca_grp_1_intact$Wetting))))+
   scale_shape_manual(values = c(1, 2, 19, 17))+
   scale_color_manual(values = pal)+
   labs(shape="",
        title = "1.5 kPa INTACT")+
   NULL

## 4. 50 & Homogenized ----
relabund_pca_num_50_Homogenized = 
   relabund_pca %>% 
   filter(Suction==50 & Homogenization=="Homogenized") %>% 
   dplyr::select(.,-(1:6))

relabund_pca_grp_50_Homogenized = 
  relabund_pca %>% 
      filter(Suction==50 & Homogenization=="Homogenized") %>% 
  dplyr::select(.,(1:6)) %>% 
  dplyr::mutate(row = row_number())

pca = prcomp(relabund_pca_num_50_Homogenized, scale. = T)
#summary(pca)

ggbiplot(pca, obs.scale = 1, var.scale = 1, 
         groups = relabund_pca_grp_50_Homogenized$Amendments, ellipse = TRUE, circle = F,
         var.axes = TRUE)+
  geom_point(size=5,stroke=1, aes(color = groups, shape = interaction(as.factor(relabund_pca_grp_50_Homogenized$Moisture),
                                                                      as.factor(relabund_pca_grp_50_Homogenized$Wetting))))+
   scale_shape_manual(values = c(1, 2, 19, 17))+
   scale_color_manual(values = pal)+
   labs(shape="",
        title = "50 kPa Homogenized")+
   NULL

## 5. 15 & Homogenized ----
relabund_pca_num_15_Homogenized = 
   relabund_pca %>% 
   filter(Suction==15 & Homogenization=="Homogenized") %>% 
   dplyr::select(.,-(1:6))

relabund_pca_grp_15_Homogenized = 
  relabund_pca %>% 
      filter(Suction==15 & Homogenization=="Homogenized") %>% 
  dplyr::select(.,(1:6)) %>% 
  dplyr::mutate(row = row_number())

pca = prcomp(relabund_pca_num_15_Homogenized, scale. = T)
#summary(pca)

ggbiplot(pca, obs.scale = 1, var.scale = 1, 
         groups = relabund_pca_grp_15_Homogenized$Amendments, ellipse = TRUE, circle = F,
         var.axes = TRUE)+
  geom_point(size=5,stroke=1, aes(color = groups, shape = interaction(as.factor(relabund_pca_grp_15_Homogenized$Moisture),
                                                                      as.factor(relabund_pca_grp_15_Homogenized$Wetting))))+
   scale_shape_manual(values = c(1, 2, 19, 17))+
   scale_color_manual(values = pal)+
   labs(shape="",
        title = "15 kPa Homogenized")+
   NULL

## 6. 1.5 & intact ----
relabund_pca_num_1_Homogenized = 
   relabund_pca %>% 
   filter(Suction==1.5 & Homogenization=="Homogenized") %>% 
   dplyr::select(.,-(1:6))

relabund_pca_grp_1_Homogenized = 
  relabund_pca %>% 
      filter(Suction==1.5 & Homogenization=="Homogenized") %>% 
  dplyr::select(.,(1:6)) %>% 
  dplyr::mutate(row = row_number())

pca = prcomp(relabund_pca_num_1_Homogenized, scale. = T)
#summary(pca)

ggbiplot(pca, obs.scale = 1, var.scale = 1, 
         groups = relabund_pca_grp_1_Homogenized$Amendments, ellipse = TRUE, circle = F,
         var.axes = TRUE)+
  geom_point(size=5,stroke=1, aes(color = groups, shape = interaction(as.factor(relabund_pca_grp_1_Homogenized$Moisture),
                                                                      as.factor(relabund_pca_grp_1_Homogenized$Wetting))))+
   scale_shape_manual(values = c(1, 2, 19, 17))+
   scale_color_manual(values = pal)+
   labs(shape="",
        title = "1.5 kPa Homogenized")+
   NULL

```

</details>


---

---

## Session Info

<details>   
   <summary>click to expand</summary>

Date run: `r Sys.Date()`

```{r}
sessionInfo()
```

</details>   



