---
title: "Spatial Access -- Gas Fluxes"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      collapse = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      comment = "#>",
                      fig.path = "markdown/flux/")
```


### HYPOTHESES

- C amendments will increase CO2 flux  
   - especially in cores wet from below  

- post-rewetting CO2 flush: drought > fm for unamended soils, but drought < fm for C-amended soils

- N amendments will increase CO2 flux when wet from above

---


```{r load}
library(here)
source(here("code/0-packages.R"))
theme_set(theme_bw())

flux = read.csv(here("data/processed/flux.csv")) %>% 
  mutate(Amendments = factor(Amendments, levels = c("control", "C", "N")),
         Homogenization = factor(Homogenization, levels = c("Intact", "Homogenized")))

flux_summary = read.csv(here("data/processed/flux_summary.csv")) %>% 
  mutate(Amendments = factor(Amendments, levels = c("control", "C", "N")),
         Homogenization = factor(Homogenization, levels = c("Intact", "Homogenized")),
         Moisture = factor(Moisture, levels = c("fm", "drought")),
         Wetting = factor(Wetting, levels = c("precip", "groundw")))
```


```{r flux_corewise, eval=FALSE}
print("corewise")
flux %>% 
  ggplot(aes(x = elapsed_min_bin, y = CO2_umol_g_s))+
  geom_point()+
  facet_wrap(~ID)
```
### CUMULATIVE FLUX/CO2 EVOLVED

<details>
  <summary>stats - click to expand</summary>
  
```{r flux_aov, echo=TRUE}
aov_flux_intact = aov(log(cum_CO2C_mg) ~ Moisture*Amendments + Moisture*Wetting + Wetting*Amendments, 
                      data = flux_summary %>% filter(Homogenization=="Intact"))
summary(aov_flux_intact)

aov_flux_homo = aov(log(cum_CO2C_mg) ~ Moisture*Amendments + Moisture*Wetting + Wetting*Amendments, 
                    data = flux_summary %>% filter(Homogenization=="Homogenized"))
summary(aov_flux_homo)
```
</details>



```{r cum_flux_hsd, include=FALSE}
fit_hsd <- function(dat) {
  a <-aov(log(cum_CO2C_mg) ~ Amendments, data = dat)
  h <-agricolae::HSD.test(a,"Amendment")
  #create a tibble with one column for each treatment
  #the hsd results are row1 = drought, row2 = saturation, row3 = time zero saturation, row4 = field moist. hsd letters are in column 2
  tibble(`control` = h$groups["control",2], 
         `C` = h$groups["C",2],
         `N` = h$groups["N",2])
}  


flux_hsd = 
  flux_summary %>% 
  group_by(Moisture, Wetting, Homogenization) %>% 
  do(fit_hsd(.)) %>% 
  # retain only those with differences
  mutate(newcol = paste0(control,C,N)) %>% 
  filter(!newcol=="aaa") %>% 
  select(-newcol) %>% 
  pivot_longer(-c(Moisture, Wetting, Homogenization),
               names_to = "Amendments",
               values_to = "label")
```


```{r cum_flux_ggplot, fig.width=10, fig.height=6}
flux_cum_labels = 
  flux_summary %>% 
  na.omit() %>% 
  group_by(Moisture, Wetting, Homogenization, Amendments) %>% 
  summarize(y_lab = max(cum_CO2C_mg)) %>% 
  left_join(flux_hsd) %>% 
  na.omit()

flux_summary %>% 
  ggplot(aes(x = Amendments, y = cum_CO2C_mg))+
  geom_point(size=2)+ 
  geom_text(data = flux_cum_labels, aes(x = Amendments, y = y_lab+70, label = label))+
  #scale_color_manual(values = soilpalettes::soil_palette("redox2",3))+
  labs(title = "cumulative CO2-C evolved")+
  facet_grid(Homogenization~Moisture+Wetting)+
  theme_kp()+
  theme(panel.grid = element_blank())
```


```{r meanflux_ts, fig.width=10, fig.height=6}
# flux %>% 
#   group_by(Homogenization, Moisture, Wetting, Amendments, Assignment, elapsed_min_bin) %>% 
#   summarise(CO2_umol_g_s = mean(CO2_umol_g_s)) %>% 
#   mutate(Homogenization = factor(Homogenization, levels = c("Intact", "Homogenized"))) %>% 
#   ggplot(aes(x = elapsed_min_bin, y = CO2_umol_g_s*1000, color = Amendments))+
#   geom_path()+ #geom_point()+
#   #ylim(0, 30)+
#   facet_grid(Homogenization~Moisture+Wetting)

ggplot()+
  geom_line(stat = "smooth",
            data = flux, 
             aes(x = elapsed_min_bin, y = CO2C_mg_g_s*1000, group=CORE, color = Amendments), 
             size=0.5, geom="line", alpha = 0.5, se=FALSE, size=3)+
  geom_smooth(data = flux %>% 
                group_by(Homogenization, Moisture, Wetting, Amendments, 
                         Assignment, elapsed_min_bin) %>%
                summarise(CO2C_mg_g_s = mean(CO2C_mg_g_s)),
              aes(x = elapsed_min_bin, y = CO2C_mg_g_s*1000, color = Amendments),
              se=FALSE, size=1.5)+ #geom_point()+
  scale_color_manual(values = soilpalettes::soil_palette("redox2",3))+
  labs(title = "mean CO2-C flux",
       subtitle = "LOESS smooth")+
  facet_grid(Homogenization~Moisture+Wetting)+
  theme_kp()+
  NULL
```

---


<details>
  <summary>time series by core</summary>

```{r fluxes}
flux %>% 
  filter(Homogenization=="Intact") %>% 
  arrange(CORE, elapsed_min_bin) %>% 
  ggplot(aes(x = elapsed_min_bin, y = CO2_umol_g_s*1000, color = as.character(CORE)))+
  geom_path()+ geom_point()+
  ylim(0, 30)+
  labs(title = "intact cores")+
  theme(legend.position = "none")+
  facet_wrap(~Assignment, ncol = 3)
  
flux %>% 
  filter(Homogenization=="Homogenized") %>% 
  arrange(CORE, elapsed_min_bin) %>% 
  ggplot(aes(x = elapsed_min_bin, y = CO2_umol_g_s*1000, color = as.character(CORE)))+
  geom_path()+ geom_point()+
  ylim(0, 30)+
  labs(title = "homogenized cores")+
  theme(legend.position = "none")+
  facet_wrap(~Assignment, ncol = 3)
```





---



</details>

```{r summarytable, eval=FALSE}
flux_summarytable =
  flux_summary %>% 
  group_by(Homogenization,Assignment, Moisture, Wetting, Amendments) %>% 
  summarise(se_cum_CO2_mg = sd(cum_CO2_mg, na.rm = T)/sqrt(n()),
            cum_CO2_mg = mean(cum_CO2_mg, na.rm = T),
            se_mean_CO2_nmol_g_s = sd(mean_CO2_nmol_g_s, na.rm = T)/sqrt(n()),
            mean_CO2_nmol_g_s = mean(mean_CO2_nmol_g_s, na.rm = T)) %>% 
  mutate(cum_CO2_mg = paste(round(cum_CO2_mg,2), "\u00b1", round(se_cum_CO2_mg,2)),
         mean_CO2_nmol_g_s = paste(round(mean_CO2_nmol_g_s,2), "\u00b1", round(se_mean_CO2_nmol_g_s,2))) %>% 
  ungroup %>% 
  select(Homogenization, Assignment, Moisture, Wetting, Amendments, mean_CO2_nmol_g_s, cum_CO2_mg) 
```


```{r MEAN_FLUX, eval=FALSE}
## summary table for mean flux
flux_summarytable %>% 
  ungroup %>% 
  select(-cum_CO2_mg, -Assignment) %>% 
  spread(Amendments, mean_CO2_nmol_g_s) %>% 
  knitr::kable(align = "c")
```




```{r DUNNETT, eval=FALSE}
#### Dunnett's Test - effect of amendment  
**different from control** 
  ## stats -- Dunnett test to see if amendments increase C flux

fit_dunnett_co2_amendment <- function(dat) {
  d <-DescTools::DunnettTest((mean_CO2_nmol_g_s)~Amendments, control = "control", data = dat)
  #create a tibble with one column for each treatment
  # column 4 has the pvalue
  t = tibble(`C` = d$`control`["C-control",4], 
             `N` = d$`control`["N-control",4])
  # we need to convert significant p values to asterisks
  # since the values are in a single row, it is tricky
# t %>% 
#   # first, gather all p-values into a single column, pval
#   gather(trt, pval, 1:2) %>% 
#   # conditionally replace all significant pvalues (p<0.05) with asterisks and the rest remain blank
#   mutate(p = if_else(pval<0.05, "*","")) %>% 
#   # remove the pval column
#   dplyr::select(-pval) %>% spread(trt, p) ->
#   t
}

print("log-transformed")
flux_summary %>% 
  group_by(Homogenization, Moisture, Wetting) %>% 
  do(fit_dunnett_co2_amendment(.)) %>% 
  knitr::kable()
```


```{r meanflux, eval=FALSE}
flux_summary %>% 
  mutate(Homogenization = factor(Homogenization, levels = c("Intact", "Homogenized"))) %>% 
  ggplot(aes(x = Amendments, y = mean_CO2_nmol_g_s, color = Amendments))+
  geom_point()+
  facet_grid(Homogenization~Moisture+Wetting)+
  theme(legend.position = "none")
```


---
#### Session Info

<details>
  <summary>click to expand</summary>
  
Date run: `r Sys.Date()`

```{r}
sessionInfo()
```

</details>


