---
title: "Spatial Access -- DOC"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      collapse = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      comment = "#>",
                      fig.path = "markdown/doc/")
library(here)
source(here("code/0-packages.R"))
theme_set(theme_bw())
```

```{r}
doc = read.csv(here("data/processed/doc.csv"))  %>% 
  filter(!Suction==15) %>% 
  mutate(Amendments = factor(Amendments, levels = c("control", "C", "N")),
         Homogenization = factor(Homogenization, levels = c("Intact", "Homogenized")),
         Moisture = factor(Moisture, levels = c("fm", "drought")),
         Wetting = factor(Wetting, levels = c("precip", "groundw")))
```

```{r doc_graph, fig.width=8}
doc %>% 
  ggplot(aes(x = Amendments, y = DOC_mg_L, color = Amendments))+
  geom_point()+
  facet_grid(Homogenization+Suction~Moisture+Wetting, scales = "free_y")+
  theme(legend.position = "none")

doc %>% 
  ggplot(aes(x = Amendments, y = DOC_mg, color = Amendments))+
  geom_point()+
  facet_grid(Homogenization+Suction~Moisture+Wetting, scales = "free_y")+
  theme(legend.position = "none")
```

---

**what influenced DOC?**  

DOC in **intact** cores was influenced by:  
1. Amendments  
2. Wetting direction  
DOC in **homogenized** cores was influenced by:  
1. Amendments  
2. Wetting direction  
3. Suction  

<details>
  <summary> </summary>
```{r echo=TRUE}
summary(aov(DOC_mg ~ Amendments*Suction*Moisture*Wetting,
              data = doc %>% filter(Homogenization=="Intact")))

summary(aov(DOC_mg ~ Amendments*Suction*Moisture*Wetting,
              data = doc %>% filter(Homogenization=="Homogenized")))

```
</details>  


**how did amendments influence DOC?**  

C addition increased DOC  
N addition decreased DOC - *N stimulated consumption of DOC?*  

<details>
  <summary> </summary>
```{r echo=TRUE}
## both C and N
aov1 = aov(DOC_mg ~ Amendments, data = doc); summary(aov1)
h1 = agricolae::HSD.test(aov1, "Amendments"); h1$groups

#DescTools::DunnettTest(DOC_mg ~ Amendments, data = doc, control="control")

## excluding C
aov2 = aov(DOC_mg ~ Amendments, data = doc %>% filter(!Amendments=="C")); summary(aov2)
h2 = agricolae::HSD.test(aov1, "Amendments"); h2$groups

##

# l = nlme::lme(DOC_mg ~ Amendments*Suction*Moisture*Wetting, random = ~1|CORE, 
#               data = doc %>% filter(Homogenization=="Intact"), na.action = na.omit)
# anova(l)


```

</details>

**control soils**  


<details>
  <summary> </summary>
```{r echo=TRUE}
doc_control = doc %>% filter(Amendments=="control")

summary(aov(DOC_mg ~ Suction*Moisture,
              data = doc_control %>% filter(Homogenization=="Intact")),
        na.action=na.omit)


```

</details>
---

how much DOC was added as part of the amendment?

5 mL of 10.1 M acetate (CH3-COO-K)  
1 mole acetate = 2 mole C

10.1 M acetate = 20.2 M C = (20.2 * 12) g/L C  
5 mL of 10.1 M acetate = 0.005 L * 20.2 * 12 g/L C = `r 0.005 * 20.2 * 12` g C

---
#### Session Info

<details>
  <summary>click to expand</summary>
  
  
Date run: `r Sys.Date()`

```{r}
sessionInfo()
```

</details>
