---
title: "drake_md_report"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      collapse = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      comment = "#>",
                      fig.path = ("markdown/fticr2/"))

#source("code/0-packages.R")
library(drake)
```

---

## HYPOTHESES

- C amendments will increase diversity of SOM molecules
- C amendments will cause a depletion of aromatic molecules, especially in fine pores
- Homogenization will increase (a) total peaks, (b) diversity of peaks, (c) aromatic peaks


We selected only peaks seen in >1 of the 4 replicates (i.e. n = 2 or 3 or 4)

---

### setup
how many FTICR reps per treatment type?
```{r reps, eval=FALSE}
readd(reps) %>% 
   arrange(reps) %>% 
   knitr::kable()
```

**so we select formulae seen in at least 2 reps per treatment type**

---

## van krevelens  

<details>
  <summary>domains, baseline</summary>

### fticr domains  

```{r domains, fig.height=4, fig.width=6}
readd(gg_fticr_domains)
```

```{r vk_baseline, fig.width=5, fig.height=5}
readd(gg_fticr_baseline)
```

</details>

<details>
  <summary>VK by replication</summary>
  
  
### VK by replication

```{r vk_reps, fig.width=10, fig.height=8}
readd(gg_fticr_reps_1_5_intact)
readd(gg_fticr_reps_50_intact)
readd(gg_fticr_reps_1_5_homo)
readd(gg_fticr_reps_50_homo)
```

</details>


<details>
  <summary>VK by treatment</summary>
  
#### VK diagrams by treatment 
```{r vk_pores, fig.width=10, fig.height=5}
readd(gg_fticr_pores_1_5kPa)
readd(gg_fticr_pores_50kPa)
```

</details>



<details>
  <summary>VK unique</summary>
  
#### VK unique
unique to each amendment, in each incubation type

```{r vk_unique, fig.width=10, fig.height=5}
readd(gg_fticr_unique_int)
readd(gg_fticr_unique_homo)
```

</details>

---

### relative abundances

### STATS 

#### PERMANOVA

#### PCA 

<details>
  <summary>overall PCA</summary>
  
```{r fticr_pca_overall, fig.height=7, fig.width=15}
readd(gg_fticr_pca_intact)
readd(gg_fticr_pca_homo)
```

</details>


<details>
  <summary>PCA individual treatments</summary>
  
**individual cores**

```{r fticr_pca_indiv, fig.height=7, fig.width=15}
readd(gg_fticr_pca_intact_combined)
readd(gg_fticr_pca_homo_combined)
```

</details>


---



## Session Info

<details>   
   <summary>click to expand</summary>

Date run: `r Sys.Date()`

```{r}
sessionInfo()
```

</details>   



