---
title: "doc_report"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      collapse = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      comment = "#>",
                      fig.path = ("markdown/fticr2/"))

#source("code/0-packages.R")
library(drake)
```

```{r doc_plot1, fig.width=8}
readd(gg_doc_allpanels)
```

```{r, doc_plot2, fig.width=7}
readd(gg_doc_boxdotplot)
```

```{r doc_plot_boxplot2, fig.width=7, fig.height=10}
readd(gg_doc_boxdotplot2)
```



## what influenced DOC?

DOC was influenced by:

- Amendments
- Homogenization:Amendments
- Moisture:Amendments
- Wetting: Amendments


DOC in **intact** cores was influenced by:  
1. Amendments  
2. Moisture  


DOC in **homogenized** cores was influenced by:  
1. Amendments  
2. Moisture  
3. Suction  


<details>
  <summary>click for stats</summary>

overall ANOVA

```{r}
readd(aov_doc_all)
```

  
intact cores

```{r}
readd(aov_doc_intact)
```

homogenized cores

```{r}
readd(aov_doc_homo)
```


</details>


**how did amendments influence DOC?**  

C addition increased DOC  
N addition decreased DOC - *N stimulated consumption of DOC?*  

---

how much DOC was added as part of the amendment?

5 mL of 10.1 M acetate (CH3-COO-K)  
1 mole acetate = 2 mole C

10.1 M acetate = 20.2 M C = (20.2 * 12) g/L C  
5 mL of 10.1 M acetate = 0.005 L * 20.2 * 12 g/L C = `r 0.005 * 20.2 * 12` g C

---

#### Session Info

<details>
  <summary>click to expand</summary>
  
  
Date run: `r Sys.Date()`

```{r}
sessionInfo()
```

</details>

