---
title: "flux_drake_plan"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      collapse = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      comment = "#>",
                      fig.path = "markdown-figs/flux/")
library(drake)
```


### HYPOTHESES

- C amendments will increase CO2 flux  
   - especially in cores wet from below  

- post-rewetting CO2 flush: drought > fm for unamended soils, but drought < fm for C-amended soils

- N amendments will increase CO2 flux when wet from above

---

## stats

<details>
  <summary>stats</summary>


intact cores

```{r lme_flux_all}
readd(aov_flux_all)
```


```{r aov_flux_intact}
readd(aov_flux_intact)
```

homogenized cores

```{r aov_flux_homo}
readd(aov_flux_homo)
```

intact cores: interaction of Amendments and Moisture
```{r flux_interx_plot}
readd(flux_interx_plot)

loadd(flux_summary)

flux_summary %>% 
  filter(Homogenization=="Intact") %>% 
  group_by(Amendments, Moisture) %>% 
  dplyr::summarize(cum_CO2C_mg_gC = mean(cum_CO2C_mg_gC, na.rm = TRUE)) %>% 
  ggplot(aes(x = Amendments, y = cum_CO2C_mg_gC, color = Moisture))+
  geom_point()+ geom_path(aes(group = Moisture))+
  NULL

flux_summary %>% 
  filter(Homogenization=="Intact") %>% 
  group_by(Amendments, Moisture) %>% 
  dplyr::summarize(cum_CO2C_mg_gC = mean(cum_CO2C_mg_gC, na.rm = TRUE)) %>% 
  ggplot(aes(x = Amendments, y = cum_CO2C_mg_gC, color = Moisture))+
  geom_path(aes(group = Moisture))+
  geom_point(data = flux_summary %>% filter(Homogenization=="Intact"), 
             aes(x = Amendments, y = cum_CO2C_mg_gC, color = Moisture))+
  NULL
```

</details>


Homogenization:  

- interactive response with Amendment  
- Homogenization increased respiration in the control soils  
- Homogenization decreased respiration in the amended soils 


For intact cores,  

- respiration was influenced by Moisture:Amendments  
    - drought+rewetting increased flux for control soils only
    - for +C/+N amended soils, drought did not have a strong effect
    
- C-amendments increased respiration in FM soils  
- N-amendments increased respiration only in FM-precip soils


## graphs 

```{r cum_flux_boxplot, fig.width=5, fig.height=5}
readd(gg_flux_cum_intact_boxplot)
```


- drought increased respiration only in control soils
  - microbes limited by substrate as well as N, which were released during drought?
  - the C/N amendments alleviated these limitations, and therefore drought did not alter mineralization 
- in the drought soils, precip had more min than groundw, but only in  control soils
  - possibly because there was more C available in the top 3 cm, which stimulated respiration when rewet.
  - but when we consider all the amendments, this effect of wetting direction is lost
- fm soils, on the other hand, showed greater response to amendments
  - possibly because less C was available, and therefore microbes were more limited
  - N??
 
```{r cum_flux_homo, fig.width=10, fig.height=4}
readd(gg_cumflux_homo)
```

```{r cum_flux_ggplot, fig.width=10, fig.height=6, eval=F}
readd(gg_flux_cum)
```

```{r meanflux_ts, fig.width=10, fig.height=6}
readd(gg_flux_ts)
```


<details>
  <summary>time series by core</summary>
  
```{r corewise_flux}
readd(gg_flux_ts_core_intact)

readd(gg_flux_ts_core_homo)
```

</details>


## summary table 
cumulative CO2-C, mgC/g soil
```{r summarytable}
readd(flux_summarytable) %>% 
  dplyr::select(-Assignment) %>% 
  spread(Amendments, cum_CO2C_mg_gC) %>% 
  knitr::kable(align = "c")
```

  

---
#### Session Info

<details>
  <summary>click to expand</summary>
  
Date run: `r Sys.Date()`

```{r}
sessionInfo()
```

</details>


```{r, eval=FALSE}
flux_boxplotlabel = tribble(
  ~x, ~y, ~Moisture, ~label,
  1.5, 20, "fm", "p = 0.056",
  1.5, 20, "drought", "p = 0.11",
  1, 600, "fm", "a",
  1.18, 500, "fm", "a",
  0.82, 180, "fm", "b",
  2, 430, "fm", "a",
  2.18, 180, "fm", "b",
  1.82, 180, "fm", "ab"
) %>% 
  dplyr::mutate(Moisture = factor(Moisture, levels = c("fm", "drought")))

flux_summary %>% 
  filter(Homogenization=="Intact") %>% 
  ggplot(aes(x = Wetting, y = cum_CO2C_mg_gC))+
  geom_boxplot(width=0.5, fill = "grey90", color = "grey60", alpha = 0.3)+
  geom_point(size=4, stroke=1, position = position_dodge(width = 0.5), 
             aes(fill = Amendments, shape = Amendments))+ 
  scale_shape_manual(values = c(21, 22, 23))+
  scale_fill_manual(values = rev(soilpalettes::soil_palette("rendoll",5)))+
  labs(title = "cumulative CO2-C evolved")+
  #annotate("text", label = "p = xx", x = 1.5, y = 20)+
  geom_text(data = flux_boxplotlabel, aes(x = x, y = y, label = label), size=5)+
  facet_grid(.~Moisture)+
  theme_kp()+
  theme(panel.grid = element_blank())

```

