---
title: "flux_drake_plan"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      collapse = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      comment = "#>",
                      fig.path = "markdown/flux/")
library(drake)
```


### HYPOTHESES

- C amendments will increase CO2 flux  
   - especially in cores wet from below  

- post-rewetting CO2 flush: drought > fm for unamended soils, but drought < fm for C-amended soils

- N amendments will increase CO2 flux when wet from above

---

## stats

<details>
  <summary>stats</summary>


intact cores

```{r}
readd(aov_flux_intact)
```

homogenized cores

```{r}
readd(aov_flux_homo)
```

</details>


Homogenization:  
- interactive response with Amendment  
- Homogenization increased respiration in the control soils  
- Homogenization decreased respiration in the amended soils 


For intact cores,  
- respiration was influenced by Moisture:Amendments  
- C-amendments increased respiration in FM soils  
- N-amendments increased respiration only in FM-precip soils


## graphs 
```{r cum_flux_ggplot, fig.width=10, fig.height=6}
readd(gg_flux_cum)
```

```{r meanflux_ts}
readd(gg_flux_cum_ts)
```


<details>
  <summary>time series by core</summary>
  
```{r}
readd(gg_flux_ts_core_intact)

readd(gg_flux_ts_core_homo)
```

</details>


## summary table 

```{r}
readd(flux_summarytable) %>% 
  dplyr::select(-Assignment) %>% 
  spread(Amendments, cum_CO2C_mg) %>% 
  knitr::kable(align = "c")
```

  

---
#### Session Info

<details>
  <summary>click to expand</summary>
  
Date run: `r Sys.Date()`

```{r}
sessionInfo()
```

</details>
