---
title: "flux_drake_plan"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      collapse = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      comment = "#>",
                      fig.path = "markdown/flux/")
library(drake)
```


### HYPOTHESES

- C amendments will increase CO2 flux  
   - especially in cores wet from below  

- post-rewetting CO2 flush: drought > fm for unamended soils, but drought < fm for C-amended soils

- N amendments will increase CO2 flux when wet from above

---

## stats

<details>
  <summary>stats</summary>


intact cores

```{r aov_flux_intact}
readd(aov_flux_intact)
```

homogenized cores

```{r aov_flux_homo}
readd(aov_flux_homo)
```

intact cores: interaction of Amendments and Moisture
```{r flux_interx_plot}
readd(flux_interx_plot)
```

</details>


Homogenization:  

- interactive response with Amendment  
- Homogenization increased respiration in the control soils  
- Homogenization decreased respiration in the amended soils 


For intact cores,  

- respiration was influenced by Moisture:Amendments  
    - drought+rewetting increased flux for control soils only
    - for +C/+N amended soils, drought did not have a strong effect
    
- C-amendments increased respiration in FM soils  
- N-amendments increased respiration only in FM-precip soils


## graphs 

```{r cum_flux_boxplot, fig.width=8, fig.height=5}
readd(gg_flux_cum_intact_boxplot)
```


- drought increased respiration only in control soils
  - microbes limited by substrate as well as N, which were released during drought?
  - the C/N amendments alleviated these limitations, and therefore drought did not alter mineralization 
- in the drought soils, precip had more min than groundw, but only in  control soils
  - possibly because there was more C available in the top 3 cm, which stimulated respiration when rewet.
  - but when we consider all the amendments, this effect of wetting direction is lost
- fm soils, on the other hand, showed greater response to amendments
  - possibly because less C was available, and therefore microbes were more limited
  - N??
 

```{r cum_flux_ggplot, fig.width=10, fig.height=6}
readd(gg_flux_cum)
```

```{r meanflux_ts, fig.width=10, fig.height=6}
readd(gg_flux_cum_ts)
```


<details>
  <summary>time series by core</summary>
  
```{r corewise_flux}
readd(gg_flux_ts_core_intact)

readd(gg_flux_ts_core_homo)
```

</details>


## summary table 

```{r summarytable}
readd(flux_summarytable) %>% 
  dplyr::select(-Assignment) %>% 
  spread(Amendments, cum_CO2C_mg) %>% 
  knitr::kable(align = "c")
```

  

---
#### Session Info

<details>
  <summary>click to expand</summary>
  
Date run: `r Sys.Date()`

```{r}
sessionInfo()
```

</details>
