---
title: "results"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      collapse = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      comment = "#>",
                      fig.path = "markdown/results/")
library(drake)

#source("code/3d-fluxes_drake_plan.R")
#source("code/4b-doc_drake_report.R")
```

# HYPOTHESES:

We hypothesized that: 

- H1. Adding soluble C would alleviate substrate limitation, whereas adding soluble N would alleviate resource limitation, resulting in increased microbial activity, i.e. **greater CO2 production**, **increased diversity in SOM compounds**, and a **relative depletion in complex/aromatic compounds**. These responses would be influenced by soil physico-chemical properties:

    - H1a. pore size: The effect of C additions would be greater in tightly-held pore water. 

    - H1b. wetting direction: The effect of C amendments would be greater in cores wet from below, due to C limitation at greater soil depths. Conversely, the effect of N amendments would be greater in cores wet from above.
    
    - H1c. antecedent moisture conditions: Respiration response to C amendments would be greater in soils previously maintained at field moist conditions, compared to soils previously subjected to drought.

- H2. Homogenization would increase the diversity and the aromaticity of pore-water DOC, and this effect would be comparable across all treatments (i.e., non-amended vs. C or N amended), regardless of resource availability.

---

We used linear mixed models to determine how our response variables responded to the treatments. Homogenization, Moisture, Wetting, Amendments, Suction were used as fixed effects in an exploratory analysis.   
Because homogenization and suction both played an important role in the amount and types of C detected, we analyzed those separately.  
Because Wetting direction did not have a significant effect, we removed it as a fixed variable throughout, and instead used it as a random variable.   

---

# RESPIRATION (core-scale results)

1. **Amendments**
    - 


1. **Homogenization** 
    - for CONTROL cores, fluxes did not differ in intact vs. homogenized
    - for C and N amended cores, fluxes were significantly lower in homogenized cores 

```{r cum_flux_boxplot, fig.width=8, fig.height=5}
readd(gg_flux_cum_intact_boxplot)
```

```{r cum_flux_homo, fig.width=12, fig.height=5}
readd(gg_cumflux_homo)+
  scale_color_manual(values = soilpalettes::soil_palette("rendoll",2))
```





---


# DOC


```{r doc_boxplot4, fig.width=7, fig.height=6}
readd(gg_doc_boxdotplot4_combined)
```


effect of homogenization

```{r doc_boxplot_homo, fig.width=8, fig.height=5}
readd(gg_doc_boxdot_homo)
```



---






# FT-ICR-MS

## total peaks
total peak counts were influenced by:

- not Homogenization
- Suction (50 > 1.5 kPa)
- Moisture (drought > fm)
- not Wetting
- Amendments (declines in N)

```{r}
readd(peakcounts_total_core)
```

In intact cores, total peak counts were influenced by:

- suction:wetting
- moisture:wetting

```{r}
readd(aov_total_peaks_intact)
```



## diversity of peaks

## complex/aromatic peaks

Aromatic peaks (i.e. complex:simple ratio) were influenced by:

- Homogenization (homogenized > intact)
- Suction (50 kPa > 1.5 kPa)
- Moisture (drought > fm)
- Amendments (control > C > N)
- not Wetting direction

```{r}
readd(aov_arom_aliph_ratio_all)
```


For intact soils, Amendment effects were greater in fine pores than in coarse pores

- in coarse pores, no effect of amendment
- in fine pores, both C and N amendments caused a relative depletion of complex compounds

```{r}
readd(gg_aliph_aromatic_intact_suction)
```

