---
title: "results"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# HYPOTHESES:

We hypothesized that: 

- H1. Adding soluble C would alleviate substrate limitation, whereas adding soluble N would alleviate resource limitation, resulting in increased microbial activity, i.e. **greater CO2 production**, **increased diversity in SOM compounds**, and a **relative depletion in complex/aromatic compounds**. These responses would be influenced by soil physico-chemical properties:

    - H1a. pore size: The effect of C additions would be greater in tightly-held pore water. 

    - H1b. wetting direction: The effect of C amendments would be greater in cores wet from below, due to C limitation at greater soil depths. Conversely, the effect of N amendments would be greater in cores wet from above.
    
    - H1c. antecedent moisture conditions: Respiration response to C amendments would be greater in soils previously maintained at field moist conditions, compared to soils previously subjected to drought.

- H2. Homogenization would increase the diversity and the aromaticity of pore-water DOC, and this effect would be comparable across all treatments (i.e., non-amended vs. C or N amended), regardless of resource availability.

---

# FT-ICR-MS

## total peaks
total peak counts were influenced by:

- not Homogenization
- Suction (50 > 1.5 kPa)
- Moisture (drought > fm)
- not Wetting
- Amendments (declines in N)

```{r}
readd(peakcounts_total_core)
```

In intact cores, total peak counts were influenced by:

- suction:wetting
- moisture:wetting

```{r}
readd(aov_total_peaks_intact)
```



## diversity of peaks

## complex/aromatic peaks

Aromatic peaks (i.e. complex:simple ratio) were influenced by:

- Homogenization (homogenized > intact)
- Suction (50 kPa > 1.5 kPa)
- Moisture (drought > fm)
- Amendments (control > C > N)
- not Wetting direction

```{r}
readd(aov_arom_aliph_ratio_all)
```


For intact soils, Amendment effects were greater in fine pores than in coarse pores

- in coarse pores, no effect of amendment
- in fine pores, both C and N amendments caused a relative depletion of complex compounds

```{r}
readd(gg_aliph_aromatic_intact_suction)
```





# DOC

# RESPIRATION

